Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-24 papers/ms.tex
update ms

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia are yielding a new window
  on open cluster dispersal.  Here we present an analysis of a group
  stars spanning Cepheus ($l=100^\circ$) to Hercules ($l=40^\circ$),
  hereafter the Cep-Her complex.  The group includes four Kepler
  Objects of Interest:
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), 
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$), and
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$).
  The latter Neptune-sized planet is in part of the Cep-Her complex
  called the $\delta$\ Lyr\ cluster \citep{bouma_kep1627_2022}.  Here
  we focus on the former three systems, which are in other regions of
  the association.  Based on kinematic evidence from Gaia, stellar
  rotation periods from TESS, and spectroscopy, these three objects
  are also $\approx$40 million years (Myr) old.  More specifically, we
  find that Kepler-1643 is $46^{+9}_{-7}$\,Myr old, based on its
  membership in a dense sub-cluster of the complex called RSG-5.
  KOI-7368 and KOI-7913 are $36^{+10}_{-8}$\,Myr old, and are in a
  diffuse region that we call CH-2.  Based on the transit shapes and
  high resolution imaging, all three objects are most likely planets,
  with false positive probabilities of $6\times10^{-9}$,
  $4\times10^{-3}$, and $1\times10^{-4}$ for Kepler-1643, KOI-7368,
  and KOI-7913 respectively.  These planets empirically demonstrate
  that mini-Neptunes with sizes of $\sim$2 Earth radii exist at ages
  of 40 million years.
\end{abstract}

@@

Our focus is on a region of the Galaxy approximately 200 to 500\,pc
from the Sun, above the galactic plane, and spanning galactic
longitudes of roughly $40^\circ$ to $100^\circ$.  Two rich clusters in
this region are the $\delta$~Lyra cluster
\citep{stephenson_possible_1959} and RSG-5 \citep{roser_nine_2016}.
Each of these clusters was known before Gaia.  Their reported ages are
between 30 and 60\,Myr.  Early empirical evidence that these two
clusters could be part of a large and more diffuse population was
apparent in the Gaia-based photometric analysis of pre-main-sequence
stars by \citet[][see their Figures~11 and~13]{Zari2018}.  Further
kinematic connections and complexity were highlighted by
\citet{KounkelCovey2019}, who included these previously known groups
in the larger structures dubbed ``Theia~73'' and
``Theia~96''\footnote{See their visualization online at
\url{http://mkounkel.com/mw3d/mw2d.html} (accessed 15 March 2022)}.
The connection made by \citet{KounkelCovey2019} between the previously
known open clusters and the other groups in the region was made as
part of an unsupervised clustering analysis of the Gaia DR2 positions
and on-sky velocities with a subsequent manual ``stitching'' step.
Their results support the idea that there is an overdensity of 30 to
60\,Myr old stars in this region of the Galaxy.  \citet{Kerr2021}, in
a volume-limited analysis of the Gaia DR2 point-source catalog out to
one third of a kiloparsec, identified three of the nearest
sub-populations, dubbed ``Cepheus-Cygnus'', ``Lyra'', and
``Cerberus''.  \citet{Kerr2021} reported ages for each of these
subgroups between 30 and 35 Myr.

@@

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric,
$\alpha$, defined such that the group member with the smallest core
distance has $\alpha=1$, the group member with the greatest core
distance has $\alpha=0$, and weights for the other group members are
log-normally distributed between these two extremes.  After applying a
set of quality cuts on the astrometry and
photometry,\footnote{$\varpi/\sigma_\varpi>5$; $G/\sigma_{G}>50$;
$G_{\rm RP}/\sigma_{G_{RP}}>20$; $G_{\rm BP}/\sigma_{G_{BP}}>20$.}
this procedure yields $\alpha \sim \log_{10}\mathcal{N}(-1.55,0.61)$.
To visualize the results, in Figure~\ref{fig:XYZvtang} we show
12{,}436 objects with $\alpha>0.02$ as gray points, and overplot
4{,}763 objects with $\alpha>0.10$ as black points.  The previously
known $\delta$~Lyr\ cluster is visible at $(l,b)=(68^\circ,15^\circ$)
and $(v_{l'}, v_b)=(-4.5 ,-4 )\mkms$.  RSG-5 is visible at
$(l,b)=(83^\circ,6^\circ)$, $(v_{l'}, v_b)=(5.5 ,-3.5 )\mkms$.  Most
of the other subclusters, including in Cep-Cyg
($l,b=90^\circ,7^\circ$) and Cerberus ($l,b=48^\circ,18^\circ$) are
too small or dispersed to have previously been analyzed in great
detail.

@@

Color-absolute magnitude diagrams (CAMDs) of the candidate RSG-5 and
CH-2 members are shown in the upper row of Figure~\ref{fig:age}.  The
stars from the $\delta$~Lyr cluster are from
\citet{bouma_kep1627_2022}, and the field stars are from the Gaia EDR3
Catalog of Nearby Stars \citep{gaia_gcns_2021}.  To make these
diagrams, we imposed the data filtering criteria from
\citet[][Appendix B]{GaiaCollaboration2018}, which include binaries
while omitting instrumental artifacts from for instance low
photometric signal to noise, or a small number of visibility periods.
We then corrected for extinction using the
\citet{lallement_threedimensional_2018} dust
maps and the extinction
coefficients $k_X\equiv A_X/A_0$ from \citet{GaiaCollaboration2018},
assuming that $A_0 = 3.1 E(B-V)$.  This yielded a mean and standard
deviation for the reddening of $E(B-V)=0.036\pm0.002$ for RSG-5, and
$E(B-V)=0.017\pm0.001$ for CH-2.  By way of comparison, in
\citet{bouma_kep1627_2022} the same query for the $\delta$~Lyr cluster
yielded $E(B-V)=0.032\pm0.006$.  Finally, for the plots we set the
color range to best visualize the region of maximal age information
content: the pre-main-sequence.

The CAMDs show that for RSG-5, practically all of our candidate
members are on a tight pre-main-sequence locus.  This implies a false
positive rate of a few percent, at most.  By comparison, our control
sample (the $\delta$~Lyr candidates) has a false positive rate of
$\approx$12\%, based on the number of stars that photometrically
overlap with the field population, while being outliers from the bulk
cluster population.  For CH-2, our membership selection gives 27
objects in the color range displayed, and 23 of them appear to be
consistent with being on the pre-main-sequence.  This implies a false
positive rate in CH-2 of $\approx$15\%.

Figure~\ref{fig:age} also shows that most RSG-5 and CH-2 members
overlap with the $\delta$~Lyr cluster, and that the groups are
therefore roughly the same age.  To quantify this, we use the method
introduced by \citet[][their Section~6.3]{gagne_mutau_2020}.  The idea
is to fit the pre-main-sequence loci of a set of reference clusters,
and to then model the locus of the target cluster as a linear
combination of these reference cluster loci.  For our reference
clusters, we used UCL, IC\,2602, and the Pleiades, with the
memberships reported by \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively.  We adopted ages of 16\,Myr for
UCL \citep{pecaut_star_2016}, 38\,Myr for IC\,2602
\citep{david_ages_2015,randich_gaiaeso_2018}
%\footnote{ Ages for
%IC\,2602 vary from 40 to 46\,Myr based on lithium-depletion-boundary
%(LDB) measurements \citep{dobbie_ic_2010,randich_gaiaeso_2018}, and
%from 30 to 46\,Myr based on isochronal analyses
%\citep{stauffer_rotational_1997,david_ages_2015,bossini_age_2019}.},
and 112\,Myr for the Pleiades \citep{dahm_2015}.  These assumptions
and the subsequent processing steps taken to exclude field stars and
binaries were identical to those described in
\citet{bouma_kep1627_2022}.  The mean and uncertainty of the resulting
age posterior are $46^{+9}_{-7}$\,Myr for RSG-5, and
$36^{+10}_{-8}$\,Myr for CH-2.  For comparison, this procedure yields
an age for the $\delta$~Lyr cluster of $38^{+6}_{-5}$\,Myr.  The
slightly older isochronal age of RSG-5 is consistent with its location
relative to the $\delta$~Lyr cluster in the upper left panel of
Figure~\ref{fig:age}.

@@

The lower panels of Figure~\ref{fig:age} show the results.  In RSG-5,
41/47 stars have rotation periods faster than the Pleiades (87\%).
This numerator omits the two stars with periods $>$$12$\,days visible
in the lower-left panel of Figure~\ref{fig:age}.  The age
interpretation for these latter stars, particularly the $\approx$M2.5
dwarf, is not obvious.  \citet{rebull_usco_2018} for instance have
found numerous M-dwarfs with 10-12 day rotation periods at ages of
USco ($\sim$$8$\,Myr), and some may still exist at ages of LCC
($\sim$$16$\,Myr; L.~Rebull in preparation).  Regardless, given that
nearly no field star outliers seem to be present on the RSG-5 CAMD,
the fact that we do not detect rotation periods for $\approx$13\% of
stars should perhaps be taken as an indication for the fraction of
stars for which rotation periods might not be detectable, due to
{e.g.}, pole-on stars having lower amplitude starspot modulation.

@@

A few salient properties of the Kepler objects in Cep-Her can be
gleaned from Figure~\ref{fig:age}.  The stars span spectral types of
G8V (Kepler-1627) to K6V (KOI-7913 A).  The secondary in the KOI-7913
system has spectral type $\approx$K8V.  And given that a star with
Solar mass and metallicity arrives at the zero-age main sequence at
$t\approx40$ Myr \citep{choi_mesa_2016}, these stars are all in the
late stages of their pre-main-sequence contraction.

@@

To verify these parameters and to also analyze spectroscopic youth
proxies such as the Li 6708\,\AA\ doublet and H$\alpha$, we acquired
spectra.  We also acquired high resolution imaging for each system, to
constrain the existence of visual companions, including possible bound
binaries.  The system-by-system details follow, and the relevant
results are also summarized in Table~\ref{tab:sysparams}.

@@

\paragraph{Binarity}
KOI-7913 is almost certainly a binary.  The north-west primary is
$\approx$0.5 magnitudes brighter than the south-east secondary in
optical passbands.  The two stars are separated in Gaia EDR3 by
$3\farcs5$ on-sky, and have parallaxes consistent within $1$-$\sigma$
(with an average $\varpi=3.66 \pm 0.01$\,mas).  The apparent on-sky
separation is $959 \pm 2$ au.  The Gaia EDR3 proper motions are also
nearly identical.  Since two stars were resolved in the Kepler Input
Catalog and are roughly one Kepler pixel apart, an accurate crowding
metric has already been applied in the NASA Ames data products to
correct the mean flux level \citep{2017ksci.rept....6M}.  This is
important for deriving accurate transit depths.

@@

\paragraph{High-Resolution Imaging}
We acquired adaptive optics imaging of KOI-7913 on the night of 2020
Aug 27 using the NIRC2 imager.  The observational configuration and
reduction were identical as before.  The images showed KOI-7913 A,
KOI-7913 B, and an additional faint star $\approx$$0\farcs99$ due East
of KOI-7913 B.  Applying the PSF-fitting routines from
\citet{kraus_impact_2016}, the tertiary star has a separation $\rho =
4397 \pm 3$\,mas from the primary, at a position angle $231.17^\circ
\pm 0.02^\circ$, with $\Delta K' = 6.97 \pm 0.04$.  While it is too
faint to affect the interpretation of the KOI itself, it would be
amusing if the faint neighbor were also comoving and young -- at the
age of the system, it would have a mass roughly between 10 and
15\,M$_{\rm Jup}$.  Additional imaging epochs will tell.

@@

In the future, it may be possible to obtain independent evidence for
the Cep-Her planets to directly confirm their planetary nature, for
instance through transit observations using a high-resolution
spectrograph.  For now, it is of interest whether the transit signals
might be astrophysical false positives, or whether they can be argued
to be planetary on a statistical basis.  We adopt the Bayesian
framework implemented in \texttt{VESPA} to assess the relevant
probabilities \citep{morton_efficient_2012,vespa_2015}.  Briefly
summarized, the priors in \texttt{VESPA} assume the binary star
occurrence rate from \citet{raghavan_survey_2010}, direction-specific
star counts from \citet{girardi_star_2005}, and planet occurrence
rates as described by \citet[][Section~3.4]{morton_efficient_2012}.
The likelihoods are then evaluated by forward-modeling a synthetic
population of eclipsing bodies for each astrophysical model class, in
which each population member has a known trapezoidal eclipse depth,
total duration, and ingress duration.  These summary statistics are
then compared against the actual photometric data to evaluate the
probabilities of false positive scenarios such as foreground eclipsing
binaries, hierarchical eclipsing binaries, and background eclipsing
binaries.

@@

Intriguingly, Kepler-1643 formally failed one of the data validation
centroid shift tests (see the \texttt{q1\_q17\_dr25\_koi} data
release): the angular distance between the target star's catalog
position and the position of the transiting source was measured as
$1\farcs0$ at 4.4-$\sigma$.  The reports show however that two
outlying quarters (2 and 6) drive the offset -- the centroid locations
from the other Kepler quarters are consistent at $\lesssim 0\farcs4$.
Nonetheless, this is an instructive exercise in how stellar
variability complicates centroid-based vetting tests.  The centroid
shifts measured by these tests are determined from the in- and
out-of-transit flux-weighted centroids.  For stars with significant
spot-induced variability there is no static baseline in either the in-
or out-of-transit phases.

\paragraph{KOI-7368}
KOI-7368.01 is listed on the NASA Exoplanet Archive as a ``candidate''
planet.  \citet{morton_false_2016} did not compute a false positive
probability for the system because their default trapezoidal fitting
routine failed, presumably due to the spot-induced variability.  Our
fitting approach rectifies this point, and our new NIRC2 images
revealed no new stellar companions.  Performing the relevant
calculation, we find ${\rm FPP} \approx 4\times10^{-3}$.  Though not
as convincing as Kepler-1643, this formally clears the usual threshold
for calling the planet statistically validated
\citep{morton_efficient_2012}.  The S/N of the transit is
$\approx$$32$, which indicates that it is unlikely to be caused by
systematic noise in the light curve (see Figure~\ref{fig:planets}).
The positional probability score also meets the requirements for
transiting sources thought to share positions with their target stars
\citep{2017ksci.rept...16B}.

@@

\paragraph{KOI-7913}
KOI-7913.01 is also currently listed on the NASA Exoplanet Archive as a
``candidate'' planet.  The canonical \citet{morton_false_2016}
analysis was of Q1-Q17 KOIs from DR24, and therefore spanned KOI-1.01
to KOI-7620.01 and omitted KOI-7913.01.  However the results of the
subsequent DR25 analysis by Morton et al.\ are listed at the NASA
Exoplanet Archive.  The relevant table gives a probability for the
system being an astrophysical false positive of $1.4\times10^{-4}$,
with the most likely false positive scenario being a blended eclipsing
binary.  Repeating the calculation with our new detrending and
contrast curves, we find a similar result: ${\rm FPP} =
1.3\times10^{-4}$.  Though the transit has the lowest S/N of any of
the objects discusssed (${\rm S/N}=14$), its lower FPP relative to
KOI-7368 can be understood through its relatively flat-bottomed shape,
combined with its long transit duration relative to plausible
eclipsing binary models (Figure~\ref{fig:planets}).  The host star
probability usability score \citep{2017ksci.rept...16B} also meets the
usual threshold, and so the planet seems to be validated.  Its
disposition has however previously fluctuated from ``false positive''
to ``candidate''.  The most likely explanation is the presence of
KOI-7913~B, which is located approximately one Kepler pixel away from
Kepler-7913 A (see Appendix~\ref{app:koi7913}).  Our pixel-level
analysis of the target pixel files did not show any evidence to
support the idea that KOI-7913~B could host the transiting planet.
Our NIRC2 imaging similarly ruled out the possibility of any other
plausible host star for the planet other than KOI-7913~A.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
    Planets younger than a gigayear with ages more precise than a
    factor of three are emphasized. The Cep-Her planets are
    Kepler-1643~b ($\square$), KOI-7368~b ($\triangledown$),
    KOI-7913~Ab (X), and Kepler-1627~Ab (+).  Interesting trends in
    the population of young planets currently include {\it i)} their
    large sizes and {\it ii)} the lack of young hot Jupiters.  The new
    objects of interest in Cep-Her have normal mini-Neptune sizes
    between 2 and 3\,$R_\oplus$, which is a novelty given their ages.
    Parameters are from the NASA Exoplanet Archive (2022 Apr 5).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

We have showed that Kepler-1643~b, KOI-7368~b, and KOI-7913~Ab are 40
to 50 million years old, and that each system is most likely
planetary.  The evidence for the planetary interpretation comes from
an application of \texttt{VESPA} to the Kepler data, alongside new
imaging from NIRC2.  The validity of the \texttt{VESPA} framework
rests on the premise that non-astrophysical false positives can be
rejected.  Kepler-1643 and KOI-7368 both pass all but one of the
canonical vetting tests: the check for centroid offsets between the in
and out-of-transit phases.  For both cases, the weak observed shifts
seem to be caused by starspot-induced variability in specific quarters
spuriously moving the stellar center-of-light.  Independently, our
imaging rules out companion stars at the brightness and positions that
would be needed to explain the reported shifts.

>>>>

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia are yielding a new window
  on open cluster dispersal.  Here we present an analysis of a group
  stars spanning Cepheus ($l=100^\circ$) to Hercules ($l=40^\circ$),
  hereafter the Cep-Her complex.  The group includes four Kepler
  Objects of Interest:
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), 
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$), and
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$).
  The latter Neptune-sized planet is in part of the Cep-Her complex
  called the $\delta$\ Lyr\ cluster \citep{bouma_kep1627_2022}.  Here
  we focus on the former three systems, which are in other regions of
  the association.  Based on kinematic evidence from Gaia, stellar
  rotation periods from TESS, and spectroscopy, these three objects
  are also $\approx$40 million years (Myr) old.  More specifically, we
  find that Kepler-1643 is $46^{+9}_{-7}$\,Myr old, based on its
  membership in a dense sub-cluster of the complex called RSG-5.
  KOI-7368 and KOI-7913 are $36^{+10}_{-8}$\,Myr old, and are in a
  diffuse region that we call CH-2.  Based on the transit shapes and
  high resolution imaging, all three objects are most likely planets,
  with false positive probabilities of $6\times10^{-9}$,
  $4\times10^{-3}$, and $1\times10^{-4}$ for Kepler-1643, KOI-7368,
  and KOI-7913 respectively.  These planets demonstrate
  that mini-Neptunes with sizes of $\sim$2 Earth radii exist at ages
  of 40 million years.
\end{abstract}

@@

Our focus is on a region of the Galaxy 200 to 500\,pc
from the Sun, above the galactic plane, and spanning galactic
longitudes of $40^\circ$ to $100^\circ$.  Two rich clusters in
this region are the $\delta$~Lyra cluster
\citep{stephenson_possible_1959} and RSG-5 \citep{roser_nine_2016}.
Each of these clusters was known before Gaia.  Their reported ages are
between 30 and 60\,Myr.  Early empirical evidence that these two
clusters could be part of a large and more diffuse population was
apparent in the Gaia-based photometric analysis of pre-main-sequence
stars by \citet[][see their Figures~11 and~13]{Zari2018}.  Further
kinematic connections and complexity were highlighted by
\citet{KounkelCovey2019}, who included these previously known groups
in the larger structures dubbed ``Theia~73'' and
``Theia~96''\footnote{See their visualization online at
\url{http://mkounkel.com/mw3d/mw2d.html} (accessed 15 March 2022)}.
The connection made by \citet{KounkelCovey2019} between the previously
known open clusters and the other groups in the region was made as
part of an unsupervised clustering analysis of the Gaia DR2 positions
and on-sky velocities with a subsequent manual ``stitching'' step.
Their results support the idea that there is an overdensity of 30 to
60\,Myr old stars in this region of the Galaxy.  \citet{Kerr2021}, in
a volume-limited analysis of the Gaia DR2 point-source catalog out to
one third of a kiloparsec, identified three of the nearest
sub-populations, dubbed ``Cepheus-Cygnus'', ``Lyra'', and
``Cerberus''.  \citet{Kerr2021} reported ages for each of these
subgroups between 30 and 35 Myr.

@@

The outcome of the analysis up to the point of the third step is shown
in Figure~\ref{fig:XYZvtang}.  To enable a selection cut that filters
out field-star contaminants, we also compute a weight metric,
$\alpha$, defined such that the group member with the smallest core
distance has $\alpha=1$, the group member with the greatest core
distance has $\alpha=0$, and weights for the other group members are
log-normally distributed between these two extremes.  After applying a
set of quality cuts on the astrometry and
photometry,\footnote{$\varpi/\sigma_\varpi>5$; $G/\sigma_{G}>50$;
$G_{\rm RP}/\sigma_{G_{RP}}>20$; $G_{\rm BP}/\sigma_{G_{BP}}>20$.}
this procedure yields $\alpha \sim \log_{10}\mathcal{N}(-1.55,0.61)$.
To visualize the results, in Figure~\ref{fig:XYZvtang} we show
12{,}436 objects with $\alpha>0.02$ as gray points, and 
4{,}763 objects with $\alpha>0.10$ as black points.  The previously
known $\delta$~Lyr\ cluster is visible at $(l,b)=(68^\circ,15^\circ$)
and $(v_{l'}, v_b)=(-4.5 ,-4 )\mkms$.  RSG-5 is visible at
$(l,b)=(83^\circ,6^\circ)$, $(v_{l'}, v_b)=(5.5 ,-3.5 )\mkms$.  Most
of the other subclusters, including in Cep-Cyg
($l,b=90^\circ,7^\circ$) and Cerberus ($l,b=48^\circ,18^\circ$) are
too small or dispersed to have previously been analyzed in great
detail.

@@

Color-absolute magnitude diagrams (CAMDs) of the candidate RSG-5 and
CH-2 members are shown in the upper row of Figure~\ref{fig:age}.  The
stars from the $\delta$~Lyr cluster are from
\citet{bouma_kep1627_2022}, and the field stars are from the Gaia EDR3
Catalog of Nearby Stars \citep{gaia_gcns_2021}.  To make these
diagrams, we imposed the data filtering criteria from
\citet[][Appendix B]{GaiaCollaboration2018}, which include binaries
while omitting artifacts from for instance low
photometric signal to noise, or a small number of visibility periods.
We then corrected for extinction using the
\citet{lallement_threedimensional_2018} dust
maps and the extinction
coefficients $k_X\equiv A_X/A_0$ from \citet{GaiaCollaboration2018},
assuming that $A_0 = 3.1 E(B-V)$.  This yielded a mean and standard
deviation for the reddening of $E(B-V)=0.036\pm0.002$ for RSG-5, and
$E(B-V)=0.017\pm0.001$ for CH-2.  By way of comparison, in
\citet{bouma_kep1627_2022} the same query for the $\delta$~Lyr cluster
yielded $E(B-V)=0.032\pm0.006$.  Finally, for the plots we set the
color range to best visualize the region of maximal age information
content: the pre-main-sequence.

The CAMDs show that for RSG-5, all but one of the candidate
members are on a tight pre-main-sequence locus.  This implies a false
positive rate of a few percent, at most.  By comparison, our control
sample (the $\delta$~Lyr candidates) has a false positive rate of
$\approx$12\%, based on the number of stars that photometrically
overlap with the field population, while being outliers from the bulk
cluster population.  For CH-2, our membership selection gives 27
objects in the color range displayed, and 23 of them appear to be
consistent with being on the pre-main-sequence.  This implies a false
positive rate in CH-2 of $\approx$15\%.

Figure~\ref{fig:age} also shows that most RSG-5 and CH-2 members
overlap with the $\delta$~Lyr cluster, and that the groups are
therefore roughly the same age.  To quantify this, we use the method
introduced by \citet[][their Section~6.3]{gagne_mutau_2020}.  The idea
is to fit the pre-main-sequence loci of a set of reference clusters,
and to then model the locus of the target cluster as a linear
combination of these reference cluster loci.  For our reference
clusters, we used UCL, IC\,2602, and the Pleiades, with the
memberships reported by \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively.  We adopted ages of 16\,Myr for
UCL \citep{pecaut_star_2016}, 38\,Myr for IC\,2602
\citep{david_ages_2015,randich_gaiaeso_2018}
%\footnote{ Ages for
%IC\,2602 vary from 40 to 46\,Myr based on lithium-depletion-boundary
%(LDB) measurements \citep{dobbie_ic_2010,randich_gaiaeso_2018}, and
%from 30 to 46\,Myr based on isochronal analyses
%\citep{stauffer_rotational_1997,david_ages_2015,bossini_age_2019}.},
and 112\,Myr for the Pleiades \citep{dahm_2015}.  These assumptions
and the subsequent processing steps taken to exclude field stars and
binaries were identical to those described in
\citet{bouma_kep1627_2022}.  The mean and uncertainty of the resulting
age posterior are $46^{+9}_{-7}$\,Myr for RSG-5, and
$36^{+10}_{-8}$\,Myr for CH-2.  For comparison, this procedure yields
an age for the $\delta$~Lyr cluster of $38^{+6}_{-5}$\,Myr.  The
older isochronal age of RSG-5 is consistent with its location
relative to the $\delta$~Lyr cluster in the upper left panel of
Figure~\ref{fig:age}.

@@

The lower panels of Figure~\ref{fig:age} show the results.  In RSG-5,
41/47 stars have rotation periods faster than the Pleiades (87\%).
This numerator omits the two stars with periods $>$$12$\,days visible
in the lower-left panel of Figure~\ref{fig:age}.  The age
interpretation for these latter stars, particularly the $\approx$M2.5
dwarf, is not obvious.  \citet{rebull_usco_2018} for instance have
found numerous M-dwarfs with 10-12 day rotation periods at ages of
USco ($\sim$$8$\,Myr), and some may still exist at ages of LCC
($\sim$$16$\,Myr; L.~Rebull in preparation).  Regardless, since
nearly no field star outliers seem to be present on the RSG-5 CAMD,
the fact that we do not detect rotation periods for $\approx$13\% of
stars should perhaps be taken as an indication for the fraction of
stars for which rotation periods might not be detectable, due to
{e.g.}, pole-on stars having lower amplitude starspot modulation.

@@

A few salient properties of the Kepler objects in Cep-Her can be
gleaned from Figure~\ref{fig:age}.  The stars span spectral types of
G8V (Kepler-1627) to K6V (KOI-7913 A).  The secondary in the KOI-7913
system has spectral type $\approx$K8V.  And since a star with
Solar mass and metallicity arrives at the zero-age main sequence at
$t\approx40$ Myr \citep{choi_mesa_2016}, these stars are all in the
late stages of their pre-main-sequence contraction.

@@

To verify these parameters and to analyze youth
proxies such as the Li 6708\,\AA\ doublet and H$\alpha$, we acquired
spectra.  We also acquired high resolution imaging for each system, to
constrain the existence of visual companions, including possible bound
binaries.  The system-by-system details follow, and the relevant
results are also summarized in Table~\ref{tab:sysparams}.

@@

\paragraph{Binarity}
KOI-7913 is a binary.  The north-west primary is
$\approx$0.5 magnitudes brighter than the south-east secondary in
optical passbands.  The two stars are separated in Gaia EDR3 by
$3\farcs5$ on-sky, and have parallaxes consistent within $1$-$\sigma$
(with an average $\varpi=3.66 \pm 0.01$\,mas).  The apparent on-sky
separation is $959 \pm 2$ au.  The Gaia EDR3 proper motions are also
nearly identical.  Since two stars were resolved in the Kepler Input
Catalog and are roughly one Kepler pixel apart, an accurate crowding
metric has already been applied in the NASA Ames data products to
correct the mean flux level \citep{2017ksci.rept....6M}.  This is
important for deriving accurate transit depths.

@@

\paragraph{High-Resolution Imaging}
We acquired adaptive optics imaging of KOI-7913 on the night of 2020
Aug 27 using the NIRC2 imager.  The observational configuration and
reduction were identical as before.  The images showed KOI-7913 A,
KOI-7913 B, and an additional faint star $\approx$$0\farcs99$ due East
of KOI-7913 B.  Applying the PSF-fitting routines from
\citet{kraus_impact_2016}, the tertiary star has a separation $\rho =
4397 \pm 3$\,mas from the primary, at a position angle $231.17^\circ
\pm 0.02^\circ$, with $\Delta K' = 6.97 \pm 0.04$.  While it is too
faint to affect the interpretation of the KOI itself, it would be
amusing if the faint neighbor were also comoving and young -- at the
age of the system, it would have a mass between 10 and
15\,M$_{\rm Jup}$.  Additional imaging epochs will tell.

@@

In the future, it may be possible to obtain independent evidence for
the planetary nature of the Cep-Her planets, for instance through
transit observations using a high-resolution spectrograph.  For now,
it is of interest whether the transit signals might be astrophysical
false positives, or whether they are statistically more likely to be
planetary.  We adopt the Bayesian framework implemented in
\texttt{VESPA} to assess the relevant probabilities
\citep{morton_efficient_2012,vespa_2015}.  Briefly summarized, the
priors in \texttt{VESPA} assume the binary star occurrence rate from
\citet{raghavan_survey_2010}, direction-specific star counts from
\citet{girardi_star_2005}, and planet occurrence rates as described by
\citet[][Section~3.4]{morton_efficient_2012}.  The likelihoods are
then evaluated by forward-modeling a synthetic population of eclipsing
bodies for each astrophysical model class, in which each population
member has a known trapezoidal eclipse depth, total duration, and
ingress duration.  These summary statistics are then compared against
the actual photometric data to evaluate the probabilities of false
positive scenarios such as foreground eclipsing binaries, hierarchical
eclipsing binaries, and background eclipsing binaries.

@@

Intriguingly, Kepler-1643 failed one of the data validation
centroid shift tests (see the \texttt{q1\_q17\_dr25\_koi} data
release): the angular distance between the target star's catalog
position and the position of the transiting source was measured as
$1\farcs0$ at 4.4-$\sigma$.  The reports show however that two
outlying quarters (2 and 6) drive the offset -- the centroid locations
from the other Kepler quarters are consistent at $\lesssim 0\farcs4$.
Nonetheless, this is an instructive exercise in how stellar
variability complicates centroid-based vetting tests.  The centroid
shifts measured by these tests are determined from the in- and
out-of-transit flux-weighted centroids.  For stars with significant
spot-induced variability there is no static baseline in either the in-
or out-of-transit phases.

\paragraph{KOI-7368}
KOI-7368.01 is listed on the NASA Exoplanet Archive as a ``candidate''
planet.  \citet{morton_false_2016} did not compute a false positive
probability for the system because their default trapezoidal fitting
routine failed, presumably due to the spot-induced variability.  Our
fitting approach rectifies this point, and our new NIRC2 images
revealed no new stellar companions.  Performing the relevant
calculation, we find ${\rm FPP} \approx 4\times10^{-3}$.  Though not
as convincing as Kepler-1643, this clears the usual threshold
for calling the planet statistically validated
\citep{morton_efficient_2012}.  The S/N of the transit is
$\approx$$32$, which indicates that it is unlikely to be caused by
systematic noise in the light curve (see Figure~\ref{fig:planets}).
The positional probability score also meets the requirements for
transiting sources thought to share positions with their target stars
\citep{2017ksci.rept...16B}.

@@

\paragraph{KOI-7913}
KOI-7913.01 is also currently listed on the NASA Exoplanet Archive as a
``candidate'' planet.  The canonical \citet{morton_false_2016}
analysis was of Q1-Q17 KOIs from DR24, and therefore spanned KOI-1.01
to KOI-7620.01 and omitted KOI-7913.01.  However the results of the
subsequent DR25 analysis by Morton et al.\ are listed at the NASA
Exoplanet Archive.  The relevant table gives a probability for the
system being an astrophysical false positive of $1.4\times10^{-4}$,
with the most likely false positive scenario being a blended eclipsing
binary.  Repeating the calculation with our new detrending and
contrast curves, we find a similar result: ${\rm FPP} =
1.3\times10^{-4}$.  Though the transit has the lowest S/N of any of
the objects discusssed (${\rm S/N}=14$), its lower FPP relative to
KOI-7368 can be understood through its flat-bottomed shape,
combined with its long transit duration relative to plausible
eclipsing binary models (Figure~\ref{fig:planets}).  The host star
probability usability score \citep{2017ksci.rept...16B} also meets the
usual threshold, and so the planet seems to be validated.  Its
disposition has however previously fluctuated from ``false positive''
to ``candidate''.  The most likely explanation is the presence of
KOI-7913~B, which is located approximately one Kepler pixel away from
Kepler-7913 A (see Appendix~\ref{app:koi7913}).  Our pixel-level
analysis of the target pixel files did not show any evidence to
support the idea that KOI-7913~B could host the transiting planet.
Our NIRC2 imaging similarly ruled out the possibility of any other
plausible host star for the planet other than KOI-7913~A.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
    Planets younger than a gigayear with ages more precise than a
    factor of three are emphasized. The Cep-Her planets are
    Kepler-1643~b ($\square$), KOI-7368~b ($\triangledown$),
    KOI-7913~Ab (X), and Kepler-1627~Ab (+).  Interesting trends in
    the population of young planets include {\it i)} their
    large sizes and {\it ii)} the lack of young hot Jupiters.  The new
    objects of interest in Cep-Her have normal mini-Neptune sizes
    between 2 and 3\,$R_\oplus$, which is a novelty given their ages.
    Parameters are from the NASA Exoplanet Archive (2022 Apr 5).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

We have shown that Kepler-1643~b, KOI-7368~b, and KOI-7913~Ab are 40
to 50 million years old, and that each system is most likely
planetary.  The evidence for the planetary interpretation comes from
an application of \texttt{VESPA} to the Kepler data, alongside new
imaging from NIRC2.  The validity of the \texttt{VESPA} framework
rests on the premise that non-astrophysical false positives can be
rejected.  Kepler-1643 and KOI-7368 both pass all but one of the
canonical vetting tests: the check for centroid offsets between the in
and out-of-transit phases.  For both cases, the weak observed shifts
seem to be caused by starspot-induced variability in specific quarters
spuriously moving the stellar center-of-light.  Independently, our
imaging rules out companion stars at the brightness and positions that
would be needed to explain the reported shifts.
